
\begin{acknowledgments}
The authors thank Mario Livio and Laura Chomiuk for helpful discussion
of this paper.

Financial support for this work was provided to SAR and OG by NASA
through grant HST-GO-13386 from the Space Telescope Science Institute
(STScI), which is operated by Associated Universities for Research in
Astronomy, Inc. (AURA), under NASA contract NAS 5-26555. LLRW would
like to thank Minnesota Supercomputing Institute at the University of
Minnesota for providing resources and support.  RK acknowledges
support in part by World Premier International Research Center
Initiative (WPI Initiative), MEXT, Japan, and JSPS KAKENHI Grant
Number 26800093 and 15H05892.  J.M.D acknowledges support of the
projects AYA2015-64508-P (MINECO/FEDER, UE), AYA2012-39475-C02-01 and
the consolider project CSD2010-00064 funded by the Ministerio de
Economia y Competitividad.  MJ was supported by the Science and
Technology Facilities Council (grant number ST/L00075X/1) and used the
DiRAC Data Centric system at Durham University, operated by the
Institute for Computational Cosmology on behalf of the STFC DiRAC HPC
Facility (\url{www.dirac.ac.uk}).  MJ was funded by BIS National
E-infrastructure capital grant ST/K00042X/1, STFC capital grant
ST/H008519/1, and STFC DiRAC Operations grant ST/K003267/1 and Durham
University. DiRAC is part of the National E-Infrastructure.  SHS
thanks the Max Planck Society for support through the Max Planck
Research Group. JR acknowledges support from the ERC starting grant
336736-CALENDS. The UCSC group is supported in part by NSF grant
AST-1518052 and from fellowships from the Alfred P.\ Sloan Foundation
and the David and Lucile Packard Foundation to R.J.F.


%R.J.F.\ gratefully acknowledges support from NSF grant
%AST-1518052 and the Alfred P.\ Sloan Foundation.  This supernova
%research at Rutgers University is supported by NSF CAREER award
%AST-0847157, and NASA/Keck JPL RSA 1508337 and 1520634 to SWJ.  AZ is
%supported by NASA through Hubble Fellowship grant
%\#HST-HF2-51334.001-A awarded by STScI.
\end{acknowledgments}
