\subsection{Host Galaxy}\label{sec:HostGalaxy}

To examine whether the two transients originated from the same
physical location in the source plane, we looked for differences in
the properties of the \spock host galaxy at the location of each
event.  We first used the technique of ``pixel-by-pixel'' SED
fitting\cite{Hemmati:2014} to determine rest-frame colors and stellar
properties in a single resolution element of the \HST imaging data.
For this purpose we used the deepest possible stacks of \HST images,
comprising all available data except those images where the transient
events were present.  The resulting maps of stellar population
properties are shown in Supplementary Figure~\ref{fig:HostProperties}.
Supplementary Table~\ref{tab:HostProperties} reports measurements of
the three derived stellar population properties (color, mass, age)
from host images 11.1, 11.2 and 11.3.  In 11.1 and 11.2 these
measurements were extracted from the central pixel at the location of
each of the two \spock events.  The lensing magnification here ranges
from $\mu=10$ to 200, corresponding to a size on the source plane
between 6 and 600 pc$^2$.  For host image 11.3 we report the stellar
population properties derived from the pixel at the center of the
galaxy, because the lens models do not have sufficient precision to
map the \spock locations to specific positions in image 11.3.  With a
magnification of $\sim$3 to 5, this extraction region covers roughly
2000 to 6000 pc$^2$.

The reported uncertainties for these derived stellar properties in
Table~\ref{tab:HostProperties} reflect only the measurement errors
from the SED fitting, and do not attempt to quantify potential
systematic biases.  Such biases could arise, for example, from color
differences in the background light, which is dominated by the cluster
galaxies and varies significantly across the \MACS0416 field.  Such a
bias might shift the absolute values of the parameter scales for any
given host image (e.g., making the galaxy as a whole appear bluer,
more massive, and younger). However, the gradients across any single
host image are unlikely to be driven primarily by such systematics.

Supplementary Figure~\ref{fig:HostProperties} and Supplementary
Table~\ref{tab:HostProperties} show that the measured values of the
color, stellar mass, and age at the two \spock locations are mutually
consistent. Thus, it is plausible to assume that the two positions map
back to the same physical location at the source plane.  Comparing
those two locations to the center of the galaxy as defined in image
11.3, we see only a mild tension in the rest frame $U-V$ color. This
comparison therefore cannot quantitatively rule out the possibility
that the two transient events are located at the center of the
galaxy. However, the maps shown in Supplementary Figure~\ref{fig:HostProperties} do
show a gradient in both $U-V$ color and stellar age. For both images
11.1 and 11.2 the bluest and youngest stars ($U-V\approx0.3$,
$\tau\approx280$ Myr) are localized in knots near the extreme ends of
each image, well separated from either of the \spock transient events.
In the less distorted host image 11.3 the bluer and younger stars are
concentrated near the center. Taken together, these color and age
gradients suggest that the two transients are not coincident with the
center of their host galaxy.

\input{muse_linefits}

In addition to the \HST imaging data, we also have spatially resolved
spectroscopy from the MUSE integral field data.  The only significant
spectral line feature for the \spock host is the \forbidden{O}{ii}
$\lambda\lambda$ 3726, 3729 doublet, observed at 7474 and 7478 \AA.
To examine this feature in detail, one-dimensional spectra were
extracted from the three-dimensional MUSE data cube at a series of
locations along the \spock host-galaxy arc.

Supplementary Figure~\ref{fig:MUSEOIISequence} depicts the apertures
used for these extractions, shows the observed \forbidden{O}{ii} lines
at the \spock-NW and SE positions, and compares the \forbidden{O}{ii}
line profiles to other positions along the length of the host-galaxy
arc.  At each position the lines were extracted using apertures with a
radius of $0.6''$, so adjacent extractions are not independent,
although the two extractions centered on the \spockone and -SE
positions have no overlap.

A difference in the shape of the \forbidden{O}{ii} lines or the
doublet line ratio could provide evidence for a different environment
at the two \spock locaions, which would suggest that the two events
emerged from independent sources.  For a visual test for spectral
deviations, we first constructed a mean spectrum by averaging the 1-D
spectra from five non-overlapping apertures (apertures 1, 3, 5, 7,
9). To account for differences in magnification and host-galaxy
intensity across the arc, each input spectrum was normalized at the
wavelength 7477.7 \AA, which corresponds to the center of the
$\lambda$3729 component of the \forbidden{O}{ii} emission line.  This
mean spectrum was then subtracted from the 1-D spectrum of each
aperture, producing a set of ``residual spectra,'' shown in
Supplementary Figure~\ref{fig:MUSEOIISequence} in the lower-left panel.  These
spectra show no indication of a systematic trend in the wavelength
position, shape or line ratio across the arc.  Similarly, a comparison
of the spectra from the \spock-NW and SE locations (right panels of
Supplementary Figure~\ref{fig:MUSEOIISequence}) reveals no significant difference in
the \forbidden{O}{ii} line shapes.

This qualitative comparison is borne out by a more quantitative
assessment, reported in Table~\ref{tab:MuseLineFits}. We fit a
Gaussian profile to each component of the \forbidden{O}{ii} doublet,
separately in each extracted 1-D spectrum. From these fits we measured
the integrated line flux, observed wavelength of line center
($\lambda_{\rm center}$), full width at half maximum intensity (FWHM), and the
intensity ratio of the two components of the doublet.  These
quantities---all reported in Table~\ref{tab:MuseLineFits}---do not
exhibit any discernible gradient across the host galaxy.  Thus, the
\forbidden{O}{ii} measurements from MUSE cannot be used to distinguish
either \spock location from the other, or to definitively answer
whether either position is coincident with the center of the host
galaxy (as would be required, for example, if these transients were
from an AGN).  We conclude that it is entirely plausible but not
certain that the two \spock events arose from the same physical
location in the host galaxy.

