
\subsection{Expected Timescale for Microlensing Events.}\label{sec:Microlensing}

A commonly observed example of microlensing-induced transient effects
is when a bright background source (a quasar) is magnified by a
galaxy-scale lens\citep{Wambsganss:2001, Kochanek:2004}.  In this
optically thick microlensing regime, the lensing potential along the
line of sight to the quasar is composed of many stellar-mass objects.
Each compact object along the line of sight generates a separate
critical lensing curve, resulting in a complex web of overlapping
critical curves. As all of these lensing stars are in motion relative
to the background source, the web of caustics will shift across the
source position, leading to a stochastic variability on timescales of
months to years.  This scenario is inconsistent with the observed
data, as the two \spock events were far too short in duration and did
not exhibit the repeated ``flickering'' variation that would be
expected from optically thick microlensing.

For the cluster-scale lens relevant in the case of \spock, we should
expect to be in the optically thin microlensing regime.  This
situation is similar to the ``local'' microlensing light curves
observed when stars within our Galaxy or neighboring dwarf galaxies
pass behind a massive compact halo object\citep{Paczynski:1986,
  Alcock:1993, Aubourg:1993, Udalski:1993}.  In this case, an isolated
microlensing event can occur if there is a background star (i.e., in
the \spock host galaxy) that is the dominant source of luminosity in
its environment. In practice this means that the source must be a very
bright O or B star with mass of order 10 \Msun.  Depending on its age,
the size of such a star would range from a few to a few dozen times
the size of the Sun.  The net relative transverse velocity would be on
the order of a few 100 km s$^{-1}$, which is comparable to the orbital
velocity of stars within a galaxy or galaxies within a cluster.

In the case of a smooth cluster potential, the timescale $\tau$ for
the light curve of such a caustic crossing event is dictated by the
radius of the source, $R$, and the net transverse velocity, $v$, of
the source across the caustic\citep{Chang:1979,Chang:1984,MiraldaEscude:1991} as

\begin{equation}
  \tau = \frac{6 R}{5\,\Rsun}\frac{300~{\rm km~ s}^{-1}}{v}~\rm{hr.}
\label{eqn:caustic_crossing_time}
\end{equation}

\noindent Thus, for reasonable assumptions about the star's radius and
velocity, the timescale $\tau$ is on the order of hours to days, which is well
matched to the observed rise and decline timescales of the \spock
events.
