\section{Other Astrophysical Models}

The RN explanation for the two \spock events is consistent with the
available data, but requires the source to be an extreme version of a
RN system.  It therefore behooves us to examine whether there are any
more mundane astrophysical models that can accommodate all of the
available observations.

\subsection{Stellar Explosions}

The most common category of transient sources found in deep
extragalactic surveys are SNe, and our searches of the HFF survey
fields have found dozens of SNe, including several with significant
lensing magnification \citep{Rodney:2015,Kelly:2015a}. All SNe and
SN-like transients are much brighter than RNe, so the relatively high
peak luminosity of \spock could be more easily accommodated by
invoking a SN model. However, the very rapid rise and fall of both
light curves (observation \ref{obs:timescale}) is incompatible with
any of the normal SN classes.  For both thermonuclear white dwarf
explosions (Type Ia) and the core-collapse explosions of massive stars
(Type Ib, Ic, and II) the optical light curve after reaching peak
brightness is primarily powered by the decay of radioactive
\NiFiftySix to \CoFiftySix, which leads to a minimum decline rate of
$\sim$0.1 mag day$^{-1}$.  For Type II SNe this decay time can be
extended into a plateau phase by the recession of the photosphere via
a recombination wave propagint inward through the ionized H of the
expanding outer shell.  In no case can a normal SN powered by the
\NiFiftySix decay chain exhibit the decline rate of $t_3<8$ days that
has been observed for \spock.  Furthermore, the observed peak
luminosities for both \spock events are too low for most Type I or
Type II SN, which peak at $\sim10^{42}$ to $10^{43}$ erg s$^{-1}$.

Stellar flares are another very common class of transient phenomena in
which the photosphere brightens very rapidly due to magnetic activity
in the stellar atmosphere.  We can dismiss this possibility because
the observed luminosity of both \spock events (observation
\ref{obs:luminosity}) is far too high for even the most energetic
stellar flares. The brightest flare stars release a total energy in
the range of $10^{33}$ to $10^{38}$ erg over a span of minutes to
hours \citep{Balona:2012,Karoff:2016}.

The peak luminosity is marginally compatible with several categories
of ``SN-like'' transients, such as luminous red novae, Calcium-rich
transients, kilonovae, .Ia explosions, and fast optical transients.
However, there are no examples of known transients from these
categories with a light curve that rises and declines as quickly as
the two \spock events.  Furthermore, none of these transient
categories have been observed to exhibit recurrent outbursts within a
single year. Thus, to match the two \spock events one would need to
invoke either two separate sources in the same galaxy or explain the
time separation wholly as a result of gravitational lensing.

\todo{Add references.}

\todo{Make a figure showing the light curves compared to those fast
  transient models}


\subsection{Microlensing}

In the presence of strong gravitational lensing it is possible to
generate a transient event from lensing effects alone.  In this case
the background source has a steady luminosity but the relative motion
of the source, lens, and observer causes the magnification of that
source to change rapidly with time.

A commonly observed example is the microlensing of a background quasar
by a galaxy-scale lens \citep{Wambsganss:2001, Kochanek:2004}.  In
this optically thick microlensing regime, the lensing potential along
the line of sight to the quasar is composed of many stellar-mass
objects.  Each compact object along the line of sight generates a
separate critical lensing curve, resulting in a complex web of
overlapping critical curves. As all of these lensing stars are in
motion relative to the background source, the web of caustics will
shift across the source position, leading to a stochastic variability
on timescales of months to years.  This scenario is inconsistent with
the observed data, as the two \spock events were far too short in
duration and did not exhibit the repeated ``flickering'' variation
that would be expected from optically thick microlensing.

A second possibility is through an isolated strong lensing event with
a rapid timescale, such as a background star crossing over a lensing
critical curve.  This corresponds to the optically thin microlensing
regime, and is similar to the ``local'' microlensing light curves
observed when stars within our galaxy or neighboring dwarf galaxies
pass behind a massive compact halo object \citep{Paczynski:1986,
  Alcock:1993, Aubourg:1993, Udalski:1993}.  In the case of a star
crossing the caustic of a smooth lensing potential, the amplification
of the source flux would increase (decrease) with a characteristic
$t^{-1/2}$ profile as it moves toward (away from) the caustic. This
slowly evolving light curve transitions to a very sharp decline (rise)
when the star has moved to the other side of the caustic
\citep{Schneider:1986,MiraldaEscude:1991}.  With a more complex lens
comprising many compact objects, the light curve would exhibit a
superposition of many such sharp peaks \citep{Lewis:1993}.

To generate an isolated microlensing event, the background source
would have to be the dominant source of luminosity in its environment,
meaning it must be a very bright O or B star with mass of order 10
\Msun.  Depending on its age, the size of such a star would range from
a few to a few dozen times the size of the sun.  The net relative
transverse velocity would be on the order of a few 100 km/s, which is
comparable to the orbital velocity of stars within a galaxy or
galaxies within a cluster.  \citet{MiraldaEscude:1991} showed
that---in the case of a smooth cluster potential---the
%timescale
%$\tau$ for the light curve of such a caustic crossing event is
%dictated by the radius of the source, $R$, and the net transverse
%velocity, $v$, of the source across the caustic, as:
%
%\begin{equation}
%  \tau = 6\frac{R}{5\,\Rsun}\frac{300 {\rm km~ s}^{-1}}{v}~\rm{hr}
%\label{eqn:caustic_crossing_time}
%\end{equation}
%
%
%\noindent Thus, the
characteristic timescale of such an event would be on the order of
hours or days, which is in the vicinity of the timescales observed for
the \spock events.  However, this scenario could not plausibly
generate two events with similar decay timescales at distinct
locations on the sky.  This is because a caustic-crossing transient
event must necessarily appear at the location of the lensing critical
curve, but in this case the critical curve most likely passes between
the two \spock locations. At best, a caustic crossing could account
for only one of the \spock events, not both.


\subsection{Single Explosion, Time Delayed}




\subsection{Two Separate Sources}

Invoking two separate and unrelated explosions (Scenario
\ref{case:twoexplosions}) would imply that the two events are {\it
  not} coincident at the source plane in either space or time.  This
is consistent with the lens models, which makes this scenario
initially more attractive.  However, removing the spatial coincidence
is problematic, because we must then assert that two very similar
transients independently appeared by chance in the same host galaxy in
the same year.  This assertion would be plausible if the explosions
were from a very common source, but the rapid light curve already
rules out all of the common categories of supernova explosions.  Since
we have not observed any similar fast transients in any other galaxy
throughout the Frontier Fields survey, to accept this scenario we
would have to conclude that the \spock host galaxy is a very unusual
physical environment that provided uniquely fertile ground for such
transients.

%No other \HST survey has reported a transient source with
%a light curve similar to the \spock events, meaning that these -- a
%scenario which strains credulity regardless of

%All five lens models indicate that the locations of
%the two events are within \TODO{How many arcsec?  how many pc?}.

% \TODO{Make a figure that plots the SED of this host galaxy at the two
%   spock locations and at the center of the host galaxy image 11.3.
%   Quantitatively assess the probability that the three SEDs are
%   consistent with being at the same location on the source plane. }


%\TODO{Evaluate the star formation and metallicity of this host galaxy
%  to determine whether the host is very unique.}

Nevertheless, let us accept the premise that this host has generated
two rare transients in the same year, and consider what rare
explosion categories could be separately consistent with the observed
light curves.

\TODO{Evaluate kilonova, .Ia and Fast Optical transient light curves
  compared to the Spock light curves}

\TODO{Evaluate the likelihood of two rare explosions appearing in the
  same lensed host galaxy, comparing to rates from PS1, etc.}


\subsection{Two Events from the Same Source}

The final alternative is to allow two separate explosive events
powered by the same astrophysical source (Scenario
\ref{case:recurrent}).  In this case the observed events must be
spatially coincident but not coincident in time, which is fully
consistent with all lens model constraints.  Any transient event that
appears at the \spockone\ location must also appear at the
\spocktwo\ location, separated in time by a gravitational lensing time
delay.  Our lens models suggest that the time delay would be on the
order of 10--50 days, so this scenario supposes that those
``gravitational echoes'' were simply not observed, as they landed in
one of the long periods without \HST observations on this field.

Adopting this hypothesis immediately rules out any catastrophic
explosive events---such as a supernova or neutron star merger---in
which the progenitor system is completely destroyed or disrupted. This
scenario also does not admit any of the category of {\it variable}
sources (e.g. Cepheids, RR Lyrae, or Mira variables) that exhibit
periodic changes in flux due to pulsations of the stellar photosphere
but do not have sharp, isolated transient episodes.

There are two broad categories of astrophysical sources with
recurrent explosive events that might fit this scenario.  The first is
active galactic nuclei (AGN), in which transient episodes can be
driven by clumps of matter falling onto the accretion disk of a
supermassive black hole.  The second is a recurrent stellar explosion,
such as a recurrent nova (RN) or luminous blue variable (LBV) star.
In a RN system a white dwarf star accretes matter from a close binary
companion and experiences a surface explosion that leaves the system
intact to restart the cycle.  The LBV stars are very massive evolved
stars ($\sim$10-100 \Msun) that exhibit occasional outbursts or
eruptions associated with significant mass loss episodes -- although
the exact physical mechanism for these events remains unclear.

The AGN hypothesis is disfavored principally due to the quiescence of
the \spock sources between episodes. In addition to stochastic and
brief transient events, most AGN also exhibit slower
variation on much longer timescales, which is not observed at either
of the \spock locations. Furthermore, the spectrum of the \spock host
galaxy shows none of the broad emission lines that are often (though
not always) observed in AGN.  Finally, an AGN would necessarily be
located at the center of the host galaxy.
%The severe distortion of the
%host galaxy images makes it impossible to identify the location of the
%host center in images 11.1 and 11.2 from the galaxy morphology. Any
%spatial reconstruction at the source plane from the lens models would
%not be not precise enough for a useful test.  However, since
%gravitational lensing is achromatic, if the \spock positions are
%coincident with the host galaxy center, then the color of the galaxy
%at each \spock location in images 11.1 and 11.2 should be consistent
%with the color at the center of the less distorted image 11.3.
In Figure~\ref{fig:HostGalaxyColor} and Section~\ref{sec:HostGalaxy}
we saw that there are minor differences in the host galaxy properties
(i.e. rest-frame U-V color and mean stellar age) from the \spockone
and \spocktwo locations to the center of the host galaxy at image 11.3
Although by no means definitive, this suggests that the \spock events
were not located at the physical center of the host galaxy, and
therefore are not related to an AGN.

\todo{Discuss LBV eruptions}



