\subsection{Lens Model Variations.}\label{sec:LensModelVariations}

Supplementary Figure~\ref{fig:LensModelContours} presents probability
distributions for the three magnifications and two time delay values
of interest.  These distributions were derived by combining the Monte
Carlo chains from the CATS, GLAFIC, GLEE, and ZLTM models, and
individual runs of the GRALE model, which uses a different random seed
for each run.  We applied a weight to each model to account for the
different number of model iterations used by each modeling team. All
five of these models agree that host image 11.3 is the leading image,
appearing some 3--7 years before the other two images.  The models do
not agree on the arrival sequence of images 11.1 and 11.2: some have
the NW image 11.2 as a leading image, and others have it as a trailing
image.  However, the models do consistently predict that the
separation in time between those two images should be roughly in the
range of 1 to 60 days.

Because of the proximity of the critical curves in all models, the
predicted time delays and magnification factors are significantly
different if calculated at the model-predicted positions instead of
the observed positions.  For example, in the GLEE model series (GLEE
and GLEE-var) when switching from the observed to model-predicted
positions the arrival order of the NW and SE images flips, the
expected time delay drops from tens of days to $<$1 day, and the
magnifications change by 30-60\%.  However, the expected
magnifications and time delays between the events still fall within
the broad ranges summarized in Table~\ref{tab:LensModelPredictions}
and shown in Supplementary Figure~\ref{fig:LensModelContours}.  Regardless of
whether the model predictions are extracted at the observed or
predicted positions of the \spock events, none of the lens models can
accommodate the observed 234-day time difference as purely a
gravitational lensing time delay.

We used variations of several lens models to investigate how the
lensing critical curves shift under a range of alternative assumptions
or input constraints.  These variations highlight the range of
systematic effects that might impact the model predictions for the
\spock magnifications, time delays and proximity to the critical
curves.  Figure~\ref{fig:SpockCriticalCurves} shows the critical
curves for a source at $z=1$ (the redshift of the \spock host galaxy)
predicted by our seven baseline models, plus the four variations
described below.  Within a given model, variations that move a
critical curve closer to the position of \spockone\ would drive the
magnification of that event much higher (toward $\mu_{\rm
  NW}\approx200$).  This generally also has the effect of moving the
critical curve farther from \spocktwo, which would necessarily drive
its magnification downward (toward $\mu_{\rm SE}\approx10$).

The baseline CATS model reported in
Table~\ref{tab:LensModelPredictions} corresponds to the CATSv4.1 model
published on the STScI Frontier Fields lens model repository
(\url{https://archive.stsci.edu/pub/hlsp/frontier/macs0416/models/cats/v4.1/}).
That model uses 178 cluster member galaxies, including a galaxy $<5''$
south of the \spock host galaxy, which creates a local critical curve
that intersects the \spocktwo location.  Our CATS-var model is an
earlier iteration of the model, published on the STScI repository as
CATSv4
(\url{https://archive.stsci.edu/pub/hlsp/frontier/macs0416/models/cats/v4/}),
and includes only 98 galaxies identified as cluster members.  In this
variation the nearby cluster member galaxy is not included, so the
\spocktwo event is not intersected by a critical curve. However, the
\spockone event is approximately coincident with the primary critical
curve of the \macs0416 cluster.  When the critical curve is close to
either \spock location, the magnifications predicted by the CATS model
are driven up to $\mu>100$.  However, the time delays remain small, on
the order of tens of days, and incompatible with the observed 234-day
gap.

The WSLAP-var model evaluates whether the cluster redshift
significantly impacts the positioning of the critical curve. In this
merging cluster, the northern brightest cluster galaxy (BCG) has a
slighter higher redshift than the southern BCG. The mean redshift of
the cluster is not precisely determined, since it is likely to be
aligned somewhat along the line of sight.  For the WSLAP-var model we
shift the assumed cluster redshift $z=0.4$ from the default $z=0.396$
(used in all the baseline models).  The shift in the critical curve is
noticeable, but not substantial, insofar as this change does not drive
the critical curve to intersect either or both of the \spock
locations.

The GLEE-var model is a multi-plane lens model (Chiriv{\`i} et al.,~in
prep.) that incorporates 13 galaxies with spectroscopic redshifts that
place them either in the foreground or background of the \macs0416
cluster.  Supplementary Figure~\ref{fig:LineOfSightLenses} marks these
13 galaxies and highlights two of them that appear in the foreground
of the \spock host galaxy and are close to the lines of sight to the
\spock transients. Both the foreground $z=0.0557$ galaxy and the
reconstructed position of the $z=0.9397$ galaxy have a projected
separation of $<$4\arcsec from the \spocktwo transient position.
Including these galaxies in the GLEE lensing model changes the
absolute value of the magnifications at the location of HFF14Spo-NW
(HFF14Spo-SE) to $\sim70$ ($\sim250$) and the time delay between the
two locations to $\sim50$ days.  The line-of-sight galaxies also
result in a shift of the position of the critical curve---as can be
seen by comparing the GLEE and GLEE-var models in
Figure~\ref{fig:SpockCriticalCurves}. Nonetheless, the predicted time
delays are still incompatible with the observed gap of 234 days
between events.

The GLAFIC-var model examines whether it is plausible for a critical
curve to intersect both \spock locations---contrary to the baseline
assumption of a single critical curve subtending the \spock host
galaxy roughly midway between the two positions.  This model includes
a customized constraint, requiring that the magnification factors at
the \spock positons are $>1000$.  To achieve this, we independently
adjusted the mass scaling for the two nearest cluster member galaxies,
which are located just northeast and south of the \spock host galaxy
arc.  The mass of the northeast member galaxy was increased by
$\sim$30\% and that of the southern one by $\sim$60\%.  As a simple
check of the predicted morphology of the host galaxy, we placed a
source with a simple Sersic profile\cite{Sersic:1963} on the source
plane. The lensed image of that artificial source is an unbroken
elongated arc, reproducing the host galaxy image morphology reasonably
well.

For this modification of the GLAFIC lens model to be justified in a
statistical sense, the revised model should still accurately reproduce
the observed strong-lensing constraints across the entire cluster.
The $\chi^2$ statistic for the baseline GLAFIC model is 240, with 196
degrees of freedom ($\chi^2_\nu=1.2$), and yields an Akaike
information criterion (AIC)\citep{Akaike:1974} of 676.  For the
GLAFIC-var model that forces multiple critical curves to intersect the
\spock locations, we get $\chi^2$=331 for 192 degrees of freedom
($\chi^2_\nu=1.7$) and AIC=769.  This suggests that the multiple
critical curve GLAFIC-var model is strongly disfavored by the
{\it positional} strong-lensing constraints that are used for both models.
However, we note that neither model incorporates the temporal
constraints of the observed time delay. 

A second variation of the CATS model (CATS-var2) was also used to test
the plausibility of multiple critical curves intersecting the \spock
locations.  As in the GLAFIC-var case, this model requires that
critical curves pass very near the \spock positions.  The model can
accommodate that constraint, insofar as the root mean square (RMS)
error of the best-fit model is similar to that of the CATS and
CATS-var models.  However, in this CATS-var2 model the \spock host
galaxy is predicted to be multiply-imaged 5 times. The \HST images do
not exhibit any breaks or substructure in the arc that would be
generally expected in such a situation.  

Moreover, this CATS-var2 model has strong implications for a separate
background galaxy in the vicinity of image 11.3 (system 14 in
\citeref{Caminha:2017}).  This galaxy is strongly lensed by a pair of
spectroscopically confirmed cluster member galaxies\citep{Caminha:2017}. Comparing the observed positions of the multiple
images of System 14 against the CATS-var2 model-predicted positions,
we find that this System contributes significantly to the global RMS
error for the model---indicating that the CATS-var2 model can not
accurately reproduce the multiple images of System 14.  Conversely,
when this system is removed as a model constraint, the RMS error
decreases, and the CATS-var2 model can more successfully pass the
critical line through the two \spock locations.  A possible
interpretation of this is that the established strong lensing
constraints (especially System 14) are incompatible with the
requirement that multiple critical curves must intersect the two
\spock locations.

